Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 conclusion.tex
minor corrections and fixes in 5 and 7.

>>>>

HEP was amongst the first, if not the very first experimental community to
realize the importance of using WMS to manage their computational campaign(s).
As computing become increasingly critical for a range of experiments, the
impact of WMS on HEP foreshadows the importance of WMS for other experiments
(such as SKA, LSST etc.) and their computational campaigns. These experiments
will have their own workload characteristics, resources types and federation
constraints, as well metrics of performance.  The design and experience
captured in this paper should prove invaluable for designing computational
campaigns and will provide a baseline to evaluate the relative merits of
different approaches.

Thanks to the efforts captured in this paper, the time-averaged utilization of
Titan has consistently been upwards of 90\%. Compare this to the time averaged
utilization of other similar leadership machines such as NSF's flagship Blue
Waters, where the average utilization fluctuates between 60-80\% (XDMoD)
machine~\cite{bw-sucks}. These impressive if not unprecedented efficiency
gains aside, this work is just a starting point towards more effective
operational models for future leadership and online analytical platforms\cite
{foap-url}. These platforms will have to support ever increasing complex
workloads with varying models for dynamic resource federation. Recent efforts
with Google Cloud for the CMS experiment -- HEPCloud~\cite{hepcloud,google-
hep} represent similar yet different approaches to dynamic resource
federation.

Our experience demonstrated the advantages arising from a  systems engineering
and abstractions based approach, in particular the pilot abstraction. As the
type, heterogeneity and complexity of future platforms  (e.g., Exascale,
Commercial Clouds) for science increases, there will be a greater need and
emphasis on abstractions to ensure WMS can both utilize as well as support
platforms.
